The Calibration Reference Data System

### 2016-02-26 docs/paper/response.txt

===================================================

Reviewer 1

The first question in the second paragraph appears to be more
for direct information to the reviewer than request for inclusion 
in the paper. If that isn't so, we are happy to address this
there (though it seems a bit off the software issue). For HST
there is a signoff on updates by instrument teams, and there is
a committee responsible for the updates, but I don't think I would
go as far as to call it a CCB. As far as contemporaneous calibration
data, these are invariably associated with the proposal and thus
the calibration is done through associating the data with the science
data in the pipeline, and these files generally do not appear
in the CDRS (or the older CDBS). Pipelines are fed tables of the
files that belong in an association so that they know which file
to use for such a purpose.

The issue of tracability is handled by the fact that all data products
are tagged with the version of CRDS rules in their header
(the pipeline context) along with relevant software versions.
Given that, the exact same numbers should be extracted if the 
same context is given. That was one major goal of the system was 
to be able to replicate previous results (file recommendations
and otherwise), which the older system could not do. We have 
added a sentence assuring that this functionality is also repeatable
for the given context. E.g., one knows which rules file the value
was extracted from and that provides all the information one 
needs.

The comment about limiting the downloads needed for areas with
limited bandwidth is already a feature of the system. The client
library only downloads files that a pipeline invocation needs, and
these downloads will be cached for the event other datasets 
require them. No other files are automatically downloaded when it
is used in this manner. We have added a sentence to make that clear.

Section 2 comments
------------------

Paper section 3 item 1:
The main point being made was that one team may submit a change
to be tested (which could take a while), followed by another team
that has a  more urgent need for an update and tesing, yet must
await the previous test to complete. The teams operate asynchronously
so one test system isn't necessarily sufficient. But the criticism 
is a good one, and given this isn't a very important point in the
paper, we have shortened this issue to say essentially that the
test system didn't address all test needs.

page 6, substitutions.
The wording suggestions are indeed much better and have been 
made.

page 6, last paragraph
Again the suggested text is much better and has been used.

****** To do

1) box text file figures
2) improve screen shots

===================================================

Reviewer 2

### 2016-02-26 docs/paper/crds.tex
most of reviewer 1 changes, sans those for figures
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2239 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

\usepackage{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{1}
\lstset{
  basicstyle=\ttfamily,
  showstringspaces=false,
  stringstyle=\color{red},
  morecomment=[l]{/},
  commentstyle=\color{blue},
}

@@

The most critical aspect of the validation requirements for reference files
concerned the keyword values used to match datasets to the appropriate
references.  Unlike dataset parameter keywords that describe a specific
instrument configuration for one observation, reference file keywords
circumscribe range of parameter values for which the reference file applies.
In CDBS, ranges of parameter values were often represented by special values
that expand into the discrete values used to define specific instrument
configurations.  As part of submitting reference files, these special values
were combinatorially exploded into multiple database rows that represented each
possible combination of parameter values intended to match to the specified
reference file.  As an example, a dataset APERTURE keyword would describe the
specific aperture an instrument was configured to use for one observation. In
contrast, the same APERTURE keyword specified in a reference file would
describe, indirectly, the combined set of different specific APERTUREs that
reference file was intended to be used for.  When multiple parameters were used
to match datasets to references, the number of distinct rows in the CDBS
database was equal to the product of the number of specific values supported by
a particular reference file for each parameter.

@@

\begin{enumerate}
\item \textbf{Difficulty testing new reference files.} 
The use of a database essentially
limited the system to one set of rules for selecting reference files. Once a
reference file was delivered to the system, effectively the rules for selection
were modified in the operation system immediately. There were occasions when
reference files were deemed to have passed functional testing (i.e., they
performed the correct calibration for the designated cases), but were submitted
with incorrect information about which modes or dates that they should be used
for. As a result, the operational pipeline would only discover that there was a
problem when processing real data, thus resulting in having to deal with correcting
mis-processed data (or in some cases, the failure to even process). Problems in the
operational pipeline are significant disruptions requiring significant work
to correct. In the last few years a test
version of the database was created so that tests could be performed, but that
introduces synchronization and management issues to make sure what is being
tested corresponds to the previous operational version. Furthermore, if
multiple deliveries are in progress from different instruments, it introduces a
coordination issue to make sure they are either all completed together or in
sequence, which can prove constraining to the needs of each instrument as far
as testing goes.

@@

There are other cases where one mistaken submission may require a series of
resubmissions of already submitted files to correct for the effect of the wrong
submission. One such example is if one mistakenly supplies a``wildcard'' for a
parameter that should only apply to one case. In this event, all the other
reference files intended for each of the other possible parameter values must
be resubmitted. This makes the potential effects of mistakes serious and thus
requires extreme care in submission.

@@

\begin{enumerate}
\item Supporting the bestref functionality.
\item Supporting the submittion of new reference files and all the issues that
go with that.
\item Supporting format, semantic, and parameter constraint checking for both
references and rules files.  Having the capability to detect typos, duplicate 
lines, and grammatical errors in rules files. 
Having the capability to analyze basic properties
such duplicate or deleted rows,  by pseudo-mode, for supported tables files.
\item Providing utilities for making CRDS useful in: operations; for instrument
scientists that must generate and monitor reference files; and end users.
\end{enumerate}

@@

The system is centered around rules files that describe (for one version) 
how reference files should be selected for a single type of
reference file. In a general sense, the file consists of a header of sorts that
describes information about what kind of reference file that it is applied to,
what the relevant information from the dataset is needed to make that
selection, and other bookkeeping information. Following that header are the
rules. Generally these are nested sets of criteria that are used to
successively narrow down the selection until a single result is determined. It
is important to understand that there is no intrinsic limit to what structures
can be supported. If more complex cases arise, new structures can be added to
the library to support these. The following lists existing selection mechanisms. 
Examples of files will illustrate specifically these structures.

@@

\begin{description}
\item[lists of allowable alternatives:] Allowable values for parameteters
may be supplied as an \textquotesingle OR\textquotesingle
{\tt }list using {\tt |} as a separator. For example:
\texttt {({\ttfamily"}filter1{\ttfamily"}
| {\ttfamily"}filter2{\ttfamily"},...)} will allow either value to match the first
parameter.
\item[Wild Cards:] Using an {\tt \*} in a string applies familiar wildcard 
matching rules to the supplied string. For example 
\texttt {({\ttfamily"}F*122{\ttfamily"})} will
match any value starting with {\tt F} and ending with {\tt 122}
\item[Regular Expressions:] This allows matching true regular expressions,
allowing for more complex matching rules than simple wildcards permit.
\item[Literal Expressions:] A literal expression is bracketed with curly
braces {\tt \{ \}} and allows inclusion of special characters without 
special interpretation by CRDS, such as {\tt | and \*}.
\item[Relational Expressions:] Relational expressions are braketed by {\tt \#}.
These do numerical comparisons on the supplied parameter value to determine
a match. Supported comparison operators are: 
\texttt {\textgreater, \textgreater =, \textless, \textless =, == and or}. 
For example \texttt {({\ttfamily"}\# >=1 and <37",)} 
will match any number equal to or 
greater than 1 and less than 37.
\item[Between:] This is simply a more convenient way of expressing a range
than using relational expressions. E.g., equivalent to the previous example
is: \texttt{{\ttfamily"}between 1 37{\ttfamily"}}. It is inclusive of the first number.
\item[N/A:] This is equivalent to using a wildcard for the value, but with 
the difference of how weighting is used (discussed below). 
\item[NOT Expressions:] A negation of a match. 
\texttt {{\ttfamily"}not HRC{\ttfamily"}} 
is a match if the value does not match {\tt HRC}.
\item[Substitutions:] Substitutions can be defined in the header. Essentially
they result in the replacement of a string in a rules file with a different
string. This is useful in the case the string is complex and must be entered
in many different rules (e.g., it is a combination of many different 
allowable values), or it is more mnemonic to those that must maintain
the rules than the actual header values are.
\end{description}

With all these match options it is possible to write multiple items that 
match a given case. In order to allow effective defaults for general cases
while allowing specific cases to override the general case, special rule
for disambiguation in these situations have been developed. The basic idea
is that more specific matches take precedence over more general matches.
For example, if one item lists as its matching value a wildcard, and another
gives a specific value for the same parameter, the specific match takes
precedence. The precedence is handled by determining the specificity of the
match. Use of specific values, wildcards, or regular expressions increase
the specificity index, while use of N/A does not. If multiple rules match,
the one with the highest specificity index is selected

@@

\subsubsection{UseAfter}
This expects an ordered sequence of date/time values as part of the rules.
This selector finds the greates date/time value that is less than or equal
to the supplied date/time.

@@

Full documentation of the syntax and semantics of all the rmap and
context files is available on the web 
\footnote{\url{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}

@@

The system is based on these files (which we refer to rmap files since they
indicate the mapping to reference files) but also involves a hierarchy of
related files that are called context files, which provide a nested 
organizational structure corresponding to the functions at different levels. Essentially context files are
text files that define a set of related files that are to be used for
that configuration.
Instrument context files collect all the rmap files for that
instrument. This file effectively defines the versions of all the rmap files
for each reference file types that comprise the version of recommendations in
effect for that instrument. In the example of the instrument context file
shown in Figure~\ref{fig:example_instrument_context},
one can see that each distinct rmap file has a unique name. If anything
is changed in an rmap file, it gets a new name

@@

This hierarchy is designed to match that for JWST and as such is currently
designed around the current levels of hierarchy. It is a possible generalization
that would allow it to deal with arbitrary levels of heirarchy, perhaps
different in number depending on the branch taken. Achieving that would
take some modification of the bestref client functionality but is possible
without a large effort. Doing the same for the submission machinery would 
be significantly more work.

@@

One of the important goals for CRDS was to streamline the process of submitting
new files while ensuring that files are well checked before committed, at least
for common use cases for new Reference files. A completely manual approach is
outlined here before addressing more automatic schemes. For the time being, the
details of how files are actually submitted is deferred to the next section

Supposing one or more new references files of a specific type for a specific
instrument are ready to be tested and used in the operations system/:

\begin{enumerate}
\item Submit each of the reference files (with validation of each file
being part of the submission process). This is expected to generate
unique names for each of the submitted reference files.
\item Edit the rmap for that reference file type to include the necessary
changes to use these (most likely either a replacement of older versions
or the addition of time-variable ones).
\item Submit the updated rmap file (again with implied validation for
correctness)
and again, generating a new, unique rmap file name that represents the version
of the file in the system that has the desired changes.
\item Edit the instrument context file to use the new version of the rmap file.
\item Submit the updated instrument context file (with validation and 
generating a new, unique name).
\item Edit the pipeline context file to use the new version of the
instrument context file.
\item Submit the updated pipeline context file (with validation and 
generating a new, unique name).
\end{enumerate}

@@

File submission is limited to authenticated users. The home page for
authentic pages is shown in Figure~\ref{fig:authenticatedhome}.
The fully automatic
standard process is dubbed ``Batch Reference Submission'' 
in reference to submission of a group of reference 
files for one instrument,
multiple types,  and automatic certification and rules updates.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
\caption{JWST failed submission example}
\label{fig:failedsubmission}
\end{figure*}

The authenticated user begains a batch submission of files on the batch
submission page (Figure~\ref{fig:batchsubmission}) 
by identifying the local files designated as the 
files to replace existing ones (note, the local file names are not the 
names the files will have when ingested into CRDS). 
When all the updates have been identified, the submit button is clicked,
and CRDS will then validate each of the reference
files. If they all pass validation, the user will be presented the results of
the results that will be produced (e.g., the new filenames for the reference
files, rmaps and context files, and other summary information). An example of a
successful validation is shown in Figure~\ref{fig:goodsubmissionreview}.
At this point the user confirms
the submission after which they will be assigned unique names, added to the
CRDS database of reference files, sent to the STScI archive for archiving, and
placed in the disk-based repository of reference files. When the submission
process completes, the user is presented with a summary page, shown in
Figure~\ref{fig:confirmedsubmission}

@@

This is handled by using the tools that the JWST pipeline use to validate the
reference files. These are based on data models that use JSON Schema
(\citealt{JSONSchemaCore, JSONSchemaValidation, JSONHyperSchema, JSONSchemaGuide})
to define the mandatory aspects of the data expected, including all the
expected data elements (whether arrays or tables), the allowable dimensionality
and datatype, and required metadata.

The required metadata includes information on who made the reference file, how
the reference file was made and related information (CRDS will also add
standard metadata related to the submission aspects, such as when the file was
submitted.)

There are further checks on file submissions that are intended to warn regarding
suspicious changes. These changes may be valid, but likely indicate a mistake. The
following such situations raise a warning on submission:

\begin{enumerate}
\item The reversion of a file to a previous version. For example, 
if a rmap has an
existing reference file name replaced by one that is earlier in the submission
sequence that would be unusual, and the submitter is warned about this reversion.
Likewise, if instrument or pipeline contexts point to earlier rmaps or instrument
contexts respectively, that raises a warning.

@@

\textbf{Affected files utility:} Given a list of datasets, determine which ones have
been affected by a change in a pipeline context. Normally it is expected that
the relevant selection parameters for each dataset is contained in a database
to avoid having to examine the contents of each dataset. This utility needs to
run in a reasonable amount of time since it may have to do this comparison for
hundreds of thousands of datasets. The inputs to the utility is a text list of
datasets, and the two pipeline contexts being compared. The results of this
can be used to determine which datasets must be reprocessed to take advantage
of any improved reference files.

\textbf{Active reference files in a context:} List all reference files used in a
pipeline context. This indicates what files may be needed to process the
data. (possibly useful for other classes of users)

@@

\textbf{Inverse mapping:} Which rmaps and contexts use a specific reference file (e.g.,
if one finds that one was defective, identify all the pipeline contexts that
used that file so that users may be notified).

@@

\textbf{Compare retrieved data with current pipeline context:} A user has downloaded
data and wishes to see what data may need to be re-retrieved since the
reference files it used are not the currently recommended ones. A variant on
this is to update the headers of the files with the newly recommended files
(though for the JWST pipelines, this isn't normally necessary). This typically
will be run remotely and thus need network access to the CRDS server.

@@

Another improvement planned is the ability to return values other than
filenames or tuples of filenames. A common use of reference files for HST 
was to provide a table of parameters to be used by the calibration 
pipeline to tune processing to the configurations. Usually the real need
of the pipeline was just a handful of parameter values rather than
a whole file. This kind of usage resulted
in a dual-layer lookup system. CDBS would select a table (though sometimes
there was only one reference file for all cases), and then the calibration
pipeline would select a specific row in the table that matched an additional
set of selection parameters. This could be greately simplified if the 
rmap itself bypassed reference files entirely and effectively embedded
the parameters as what is returned. In this manner it would relieve 
the calibration pipeline of the need for embedding its own matching 
system in its code.

@@

For JWST, CRDS will provide a web service that can be accessed
remotely. Furthermore, the JWST calibration pipelines have been designed to
make the request directly to CRDS to determine which reference files to use and
download the file if it is not available locally. This means anyone can run the
pipeline remotely and be assured that the right reference files will be used,
and retrieved if necessary.

@@

The major challenge for HST was in translating the effective rules that existed
in the database into rmap files and ensuring that CRDS was producing the same
results. This was done by doing the recommended comparison for every dataset
in the HST archive. The generation of the rmaps was automated since the target
was constantly changing for HST because of continual reference file
updates. The cycle of generating rmaps and making the reference file comparison
for all datasets was repeated many times until CRDS went operational. This was
further complicate by the fact that the database that contained the CDBS best
references was not reliable. The differences that arose had to be further
tested with the operations bestref facility (which requires using actual
datasets thus is much slower).

@@

It is important to realize that this system has a wider range of application
than just for selecting appropriate reference files. It can act as a selector
many uses so long as the number of selections is not enormous, and the set of
selection parameter is reasonably consistent and bounded for all data
sets. Other such uses are already envisioned for JWST. For example, it will be used
to determine which calibration pipeline to run for the dataset supplied. 
So rather than supplying a reference file to use, it will supply the pipeline 
to execute (either as a name of an executable, or more exactly, a pipeline 
configuration file that the pipeline startup system uses to execute the right
pipeline). It may also be
used to aid in mapping data files to the appropriate data analysis object model
for the data analysis software.

>>>>

%%\usepackage{draftwatermark}
%%\SetWatermarkText{DRAFT}
%%\SetWatermarkScale{1}
%%\lstset{
%%  basicstyle=\ttfamily,
%%  showstringspaces=false,
%%  stringstyle=\color{red},
%%  morecomment=[l]{/},
%%  commentstyle=\color{blue},
%%}

@@

The most critical aspect of the validation requirements for reference files
concerned the keyword values used to match datasets to the appropriate
references.  Unlike dataset parameter keywords that describe a specific
instrument configuration for one observation, reference file keywords
circumscribe a range of parameter values for which the reference file applies.
In CDBS, ranges of parameter values were often represented by special values
that expand into the discrete values used to define specific instrument
configurations.  As part of submitting reference files, these special values
were combinatorially exploded into multiple database rows that represented each
possible combination of parameter values intended to match to the specified
reference file.  As an example, a dataset APERTURE keyword would describe the
specific aperture an instrument was configured to use for one observation. In
contrast, the same APERTURE keyword specified in a reference file would
describe, indirectly, the combined set of different specific APERTUREs that
reference file was intended to be used for.  When multiple parameters were used
to match datasets to references, the number of distinct rows in the CDBS
database was equal to the product of the number of specific values supported by
a particular reference file for each parameter.

@@

\begin{enumerate}
\item \textbf{Difficulty testing new reference files.} 
The use of a database essentially
limited the system to one set of rules for selecting reference files. Once a
reference file was delivered to the system, effectively the rules for selection
were modified in the operation system immediately. There were occasions when
reference files were deemed to have passed functional testing (i.e., they
performed the correct calibration for the designated cases), but were submitted
with incorrect information about which modes or dates that they should be used
for. As a result, the operational pipeline would only discover that there was a
problem when processing real data, thus resulting in having to deal with correcting
mis-processed data (or in some cases, the failure to even process). Problems in the
operational pipeline are significant disruptions requiring significant work
to correct. In the last few years a test
version of the database was created so that tests could be performed without
affecting operations, yet it still didn't satisfy all testing needs.

@@

There are other cases where one mistaken submission may require a series of
resubmissions of already submitted files to correct for the effect of the wrong
submission. One such example is if one mistakenly supplies a ``wildcard'' for a
parameter that should only apply to one case. In this event, all the other
reference files intended for each of the other possible parameter values must
be resubmitted. This makes the potential effects of mistakes serious and thus
requires extreme care in submission.

@@

\begin{enumerate}
\item Supporting the bestref functionality.
\item Supporting the submittion of new reference files and all the issues that
go with that.
\item Supporting format, semantic, and parameter constraint checking for both
references and rules files.  Having the capability to detect typos, duplicate 
lines, and grammatical errors in rules files. 
Having the capability to analyze basic properties
such as duplicate or deleted rows,  by pseudo-mode, for supported tables files.
\item Providing utilities for making CRDS useful for operations, instrument
scientists that must generate and monitor reference files, and end users.
\end{enumerate}

@@

The system is centered around rules files that describe (for one version) 
how reference files should be selected for a single type of
reference file. In a general sense, the file consists of a header of sorts that
describes information about what kind of reference file that it is applied to,
what relevant information from the dataset is needed to make that
selection, and other bookkeeping information. Following that header are the
rules. Generally these are nested sets of criteria that are used to
successively narrow down the selection until a single result is determined. It
is important to understand that there is no intrinsic limit to what structures
can be supported. If more complex cases arise, new structures can be added to
the library to support these. The following lists existing selection mechanisms. 
Examples of files will illustrate specifically these structures.

@@

\begin{description}
\item[Lists of Allowable Alternatives:] Allowable values for parameteters
may be supplied as an \textquotesingle OR\textquotesingle
{\tt }list using {\tt |} as a separator. For example:
\texttt {({\ttfamily"}filter1|filter2{\ttfamily"},...)} will allow either value to match the first
parameter.
\item[Wild Cards:] Using an {\tt *} in a string applies familiar wildcard 
matching rules to the supplied string. For example 
\texttt {({\ttfamily"}F*122{\ttfamily"})} will
match any value starting with {\tt F} and ending with {\tt 122}
\item[Regular Expressions:] This allows matching true regular expressions,
allowing for more complex matching rules than simple wildcards permit.
\item[Literal Expressions:] A literal expression is bracketed with curly
braces {\tt \{ \}} and allows inclusion of special characters without 
special interpretation by CRDS, such as {\tt | and \*}.
\item[Relational Expressions:] Relational expressions are braketed by {\tt \#}.
These do numerical comparisons on the supplied parameter value to determine
a match. Supported comparison operators are: 
\texttt {\textgreater, \textgreater =, \textless, \textless =, == and or}. 
For example \texttt {({\ttfamily"}\# >=1 and <37",)} 
will match any number equal to or 
greater than 1 and less than 37.
\item[Between:] This is simply a more convenient way of expressing a range
than using relational expressions. E.g., equivalent to the previous example
is: \texttt{{\ttfamily"}between 1 37{\ttfamily"}}. It is inclusive of the first number.
\item[N/A:] This is equivalent to using a wildcard for the value, but with 
the difference of how weighting is used (discussed below). 
\item[NOT Expressions:] A negation of a match. 
\texttt {{\ttfamily"}not HRC{\ttfamily"}} 
is a match if the value does not match {\tt HRC}.
\item[Substitutions:] Substitutions can be defined in the header. Essentially
they result in the replacement of a string in a rules file with a different
string. This is useful in the case where the string is complex and must be 
entered in many different rules (e.g., it is a combination of many different 
allowable values), or where it is more mnemonic to those that must maintain
the rules than the actual header values are.
\end{description}

With all these match options it is possible to write multiple items that 
match a given case. In order to allow effective defaults for general cases
while allowing specific cases to override the general case, special rules
for disambiguation in these situations have been developed. The basic idea
is that. The precedence is handled by determining the specificity of the
match. Use of specific values, wildcards, or regular expressions increase
the specificity index, while use of N/A does not. If multiple rules match,
the one with the highest specificity index is selected

@@

\subsubsection{UseAfter}
This expects an ordered sequence of date/time values as part of the rules.
This selector finds the greatest date/time value that is less than or equal
to the supplied date/time.

@@

Full documentation of the syntax and semantics of all the rmap and
context files is available on the web.
\footnote{\url{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}

@@

The system is based on these files (which we refer to as rmap files since they
indicate the mapping to reference files) but also involves a hierarchy of
related files that are called context files, which provide a nested 
organizational structure corresponding to the functions at different levels. Essentially context files are
text files that define a set of related files that are to be used for
that configuration.
Instrument context files collect all the rmap files for that
instrument. This file effectively defines the versions of all the rmap files
for each reference file types that comprise the version of recommendations in
effect for that instrument. In the example of the instrument context file
shown in Figure~\ref{fig:example_instrument_context},
one can see that each distinct rmap file has a unique name. If anything
is changed in an rmap file, it gets a new name

@@

This hierarchy is designed to match that for JWST and as such is currently
designed around the current levels of hierarchy. A possible generalization
of this scheme would allow arbitrary levels of heirarchy, perhaps
different in number depending on the branch taken. Achieving this would
take some modification of the bestref client functionality but is possible
without a large effort. Doing the same for the submission machinery would 
be significantly more work.

@@

One of the important goals for CRDS was to streamline the process of submitting
new files while ensuring that files are well checked before committed.
A completely manual approach is
outlined here before addressing more automatic schemes. For the time being, the
details of how files are actually submitted is deferred to the next section.

Supposing one or more new references files of a specific type for a specific
instrument are ready to be tested and used in the operations system:

\begin{enumerate}
\item Submit each of the reference files (with validation of each file
being part of the submission process). This is expected to generate
unique names for each of the submitted reference files.
\item Edit the rmap for that reference file type to include the necessary
changes to use these (most likely either a replacement of older versions
or the addition of time-variable ones).
\item Submit the updated rmap file (again with implied validation for
correctness), generating a new, unique rmap file name that represents the version
of the file in the system that has the desired changes.
\item Edit the instrument context file to use the new version of the rmap file.
\item Submit the updated instrument context file (with validation,
generating a new, unique name).
\item Edit the pipeline context file to use the new version of the
instrument context file.
\item Submit the updated pipeline context file with validation, 
generating a new, unique name.
\end{enumerate}

@@

File submission is limited to authenticated users. The home page for
authenticated users is shown in Figure~\ref{fig:authenticatedhome}.
The fully automatic
standard process is dubbed ``Batch Reference Submission'' 
in reference to submission of a group of reference 
files for one instrument,
multiple types,  and automatic certification and rules updates.

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
\caption{JWST failed submission example\newline\newline}
\label{fig:failedsubmission}
\end{figure*}

The authenticated user begins a batch submission of files on the batch
submission page (Figure~\ref{fig:batchsubmission}) 
by identifying the local files designated as the 
files to replace existing ones (note, the local file names are not the 
names the files will have when ingested into CRDS). 
When all the updates have been identified, the submit button is clicked,
and CRDS will then validate each of the reference
files. If they all pass validation, the user will be presented
the results that will be produced (e.g., the new filenames for the reference
files, rmaps and context files, and other summary information). An example of a
successful validation is shown in Figure~\ref{fig:goodsubmissionreview}.
At this point the user confirms
the submission after which they will be assigned unique names, added to the
CRDS database of reference files, sent to the STScI archive for archiving, and
placed in the disk-based repository of reference files. When the submission
process completes, the user is presented with a summary page, shown in
Figure~\ref{fig:confirmedsubmission}.

@@

This is handled by using the tools that the JWST pipeline uses to validate the
reference files. These are based on data models that use JSON Schema
(\citealt{JSONSchemaCore, JSONSchemaValidation, JSONHyperSchema, JSONSchemaGuide})
to define the mandatory aspects of the data expected, including all the
expected data elements (whether arrays or tables), the allowable dimensionality
and datatype, and required metadata.

The required metadata includes information on who made the reference file, how
the reference file was made, and related information. (CRDS will also add
standard metadata related to the submission aspects, such as when the file was
submitted.)

There are further checks on file submissions that are intended to warn the submitter
regarding
suspicious changes. These changes may be valid, but likely indicate a mistake. The
following such situations raise a warning on submission:

\begin{enumerate}
\item The reversion of a file to a previous version. For example, 
if a rmap has an
existing reference file name replaced by one that is earlier in the submission
sequence that would be unusual, the submitter is warned about this reversion.
Likewise, if instrument or pipeline contexts point to earlier rmaps or instrument
contexts respectively, that raises a warning.

@@

\textbf{Affected files utility:} Given a list of datasets, determine which ones have
been affected by a change in a pipeline context. Normally it is expected that
the relevant selection parameters for each dataset is contained in a database
to avoid having to examine the contents of each dataset. This utility needs to
run in a reasonable amount of time since it may have to do this comparison for
hundreds of thousands of datasets. The inputs to the utility is a text list of
datasets, and the two pipeline contexts being compared. The results of this
can be used to determine which datasets must be reprocessed to take advantage
of any improved reference files. This functionality is implemented as a server-side
web service.

\textbf{Active reference files in a context:} List all reference files used in a
pipeline context. This indicates what files may be needed to process the
data. (This is possibly useful for other classes of users.)

@@

\textbf{Inverse mapping:} Identify which rmaps and contexts
use a specific reference file.

@@

\textbf{Compare retrieved data with current pipeline context:} A user has downloaded
data and wishes to see what data may need to be re-retrieved since the
reference files it used are not the currently recommended ones. A variant on
this is to update the headers of the files with the newly recommended files
(though for the JWST pipelines, this isn't normally necessary). This typically
will be run remotely and thus needs network access to the CRDS server.

@@

Another improvement planned is the ability to return values other than
filenames or tuples of filenames. A common use of reference files for HST 
was to provide a table of parameters to be used by the calibration 
pipeline to tune processing to the configurations. Usually the real need
of the pipeline was just a handful of parameter values rather than
a whole file. This kind of usage resulted
in a dual-layer lookup system. CDBS would select a table (though sometimes
there was only one reference file for all cases), and then the calibration
pipeline would select a specific row in the table that matched an additional
set of selection parameters. This could be greatly simplified if the 
rmap itself bypassed reference files entirely and effectively embedded
the parameters as what is returned. In this manner it would relieve 
the calibration pipeline of the need for embedding its own matching 
system in its code. Given that the state of the rules is well defined
by pipeline contexts, replicability of the returned values is ensured 
when using the same pipeline context.

@@

For JWST, CRDS will provide a web service that can be accessed
remotely. Furthermore, the JWST calibration pipelines have been designed to
make the request directly to CRDS to determine which reference files to use and
download the file if it is not available locally. This means anyone can run the
pipeline remotely and be assured that the right reference files will be used,
and retrieved if necessary. Note that only files needed for the calibration
of a particular dataset are retrieved. There is no need to download the whole
set of reference files except in the extreme case that one is reprocessing all
of the data in the archive.

@@

The major challenge for HST was in translating the effective rules that existed
in the database into rmap files and ensuring that CRDS was producing the same
results. This was done by doing the recommended comparison for every dataset
in the HST archive. The generation of the rmaps was automated since the target
was constantly changing for HST because of continual reference file
updates. The cycle of generating rmaps and making the reference file comparison
for all datasets was repeated many times until CRDS went operational. This was
further complicated by the fact that the database that contained the CDBS best
references was not reliable. The differences that arose had to be further
tested with the operations bestref facility (which requires using actual
datasets thus is much slower).

@@

It is important to realize that this system has a wider range of application
than just for selecting appropriate reference files. It can act as a selector
for many uses as long as the number of selections is not enormous, and the set of
selection parameters is reasonably consistent and bounded for all data
sets. Other such uses are already envisioned for JWST. For example, it will be used
to determine which calibration pipeline to run for the dataset supplied. 
So rather than supplying a reference file to use, it will supply the pipeline 
to execute (either as a name of an executable, or more exactly, a pipeline 
configuration file that the pipeline startup system uses to execute the right
pipeline). It may also be
used to aid in mapping data files to the appropriate data analysis object model
for the data analysis software.
